---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# civ

<!-- badges: start -->
[![R-CMD-check](https://github.com/thomaswiemann/civ/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomaswiemann/civ/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/thomaswiemann/civ/branch/main/graph/badge.svg?token=PHB9W2TJ6S)](https://app.codecov.io/gh/thomaswiemann/civ)
[![CodeFactor](https://www.codefactor.io/repository/github/thomaswiemann/civ/badge)](https://www.codefactor.io/repository/github/thomaswiemann/civ)
<!-- badges: end -->

``civ`` is an implementation of the categorical instrumental variable estimator as proposed by Wiemann (2023). The key feature of ``civ`` is optimal instrumental variable estimation in settings with relatively few observations per category by leveraging a regularization assumption that implies existence of a latent categorical variable with fixed finite support achieving the same first stage fit as the observed instrument.

## Installation

Install the latest development version from GitHub (requires [devtools](https://github.com/r-lib/devtools) package):

```{r, eval = FALSE}
if (!require("devtools")) {
  install.packages("devtools")
}
devtools::install_github("thomaswiemann/civ", dependencies = TRUE)
```